Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-12-04 Arxiv/main.tex
Update main.tex

\subsubsection{Accuracy Bound for Improved Laplace Mechanism}
\label{subsec_accuracy_lap}
Accuracy bound for improved Laplace mechanism is obtained from the standard Laplace Mechanism by replacing the sensitivity of $\Delta \bysinfer$ with $2$.

@@

\begin{table*}[h!]
\centering
\begin{tabular}{ |c|c|c|c| } 
\hline
 c & 0 
 & $1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}$
  & $1 - 
    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
    \cdot
    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}$  \\
 \hline
 $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z ) = c} $
 & 0.39346934028 & 0.39346934028 & 0.39346934028  \\
 \hline
 $\ilapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
 & $\frac{1}{\nomalizer{\dataobs}}$ & $\frac{\exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}$ & \\
 \hline
 $\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
 &  &  & \\
 \hline
\end{tabular}
\caption{Accuracy Comparison in Theoretical}
\label{tab_acc_theo}
\end{table*}

>>>>

\subsubsection{Accuracy Bound for Improved Laplace Mechanism}
\label{subsec_accuracy_lap}
Accuracy bound for improved Laplace mechanism is obtained from the standard Laplace Mechanism by replacing the sensitivity of $\Delta \bysinfer$ with $1$ in Beta-binomial model and $2$ in Dirichlet-multinomial model.

@@

\begin{table}[h!]
\scriptsize
\centering
\begin{tabular}{ |c|c|c|c| } 
\hline
 c & 0 
 & $1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}$
  & $1 - 
    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
    \cdot
    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}$  \\
 \hline
 $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z ) = c} $
 & 0.19673467014 & 0.11932560927 & 0.07237464051 \\
 \hline
 $\ilapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
 & 0.31606027941 & 0.11627207896 & 0.04277410743 \\
 \hline
 $\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
 & $\frac{1}{\nomalizer{\dataobs}}$ & $\frac{\exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}$ & \\
 \hline
\end{tabular}
\caption{Accuracy Comparison in Theoretical}
\label{tab_acc_theo}
\end{table}

In the case when $\alpha = \beta$, there are always 2 symmetric beta distributions with the same distance from the true posterior, then we have accuracy table as:
\begin{table}[h!]
\scriptsize
\centering
\begin{tabular}{ |c|c|c|c| } 
\hline
 c & 0 
 & $1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}$
  & $1 - 
    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
    \cdot
    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}$  \\
 \hline
 $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z ) = c} $
 & 0.19673467014 & 0.31606027941 & 0.19170024978 \\
 \hline
 $\ilapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
 & 0.31606027941 & 0.43233235838 & 0.1590461864 \\
 \hline
 $\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
 & $\frac{2}{\nomalizer{\dataobs}}$ & $\frac{2 \exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}$ & \\
 \hline
\end{tabular}
\caption{Accuracy Comparison in Theoretical}
\label{tab_acc_theo}
\end{table}

The probability of getting the true posterior, or posterior with certain step from Laplace mechanism is fixed whatever the data size or prior changes.
